%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Modified by:
% Gabriel Mesquida Masana
%

\documentclass[]{resume-openfont}
\usepackage{fancyhdr}
\usepackage{bookmark}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%
% LAST UPDATED DATE
%
\lastupdated{}

%
% QR
%
% \qr{}

%
% TITLE NAME
%
\namesection{Gabriel}{Mesquida Masana}
{
  \href{mailto:gabmm@stanford.edu}{gabmm@stanford.edu}
  | +65 8869 5324
  | +34 607 80 5000
}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.3\textwidth}
  {
    \bigskip
    \fontspec{Myriad Pro Semibold}
    \fontsize{30pt}{50pt}
    \selectfont
    TL;DR
    \bigskip
  }
  %
  % EDUCATION
  %
  \section{Education}

  \subsection{MSc Telecom Engineering}
  \location{1996 | BarcelonaTech, Polytechnic University of Catalonia, Spain}
  \sectionsep{}

  \subsection{MSc Business Management}
  \location{2007 | Open Univ. Catalonia, Spain}
  \sectionsep{}

  \subsection{MBA}
  \location{2013 | Henley Business School, University of Reading, UK}
  \sectionsep{}

  \subsection{MSc Market Research}
  \location{2015 | Open Univ. Catalonia, Spain}
  \sectionsep{}

  \subsection{MSc Computer Science}
  \location{2023 | University of Bath, U.K.}
  \descript{Distinction class. Dissertation: AI for Aircraft
  Trajectory Prediction}
  \sectionsep{}

  \subsection{AI Professional Program}
  \location{2024 | Stanford Engineering, U.S.A.}
  \descript{Natural Language Processing with Deep Learning,
  Reinforcement Learning \& Deep Generative Models}
  \sectionsep{}

  \subsection{AI Graduate Certificate}
  \location{In progress | Stanford Eng., U.S.A.}
  \descript{Machine Learning, Deep Learning, Deep Reinforcement
  Learning (+1)}
  \sectionsep{}

  %
  % Certs
  %
  \section{CERTIFICATIONS}
  \cert{PMP PMI | Prince2 Practitioner | ITILv3}
  \cert{Carnegie Mellon:\@ Deep Learning}
  \cert{MIT:\@ Data Science \& ML}
  \cert{DeepLearning.AI: NN \& Deep Learning, Improving Deep NN,
    Structuring ML Projects, Convolutional NN, Sequence Models, Deep
  Learning Specialisation}
  \cert{ISC2:\@ CISSP CSSLP CSSP}
  \cert{Linux Foundation:\@ CKAD CKA CKS}
  \cert{Google Cloud:\@ GCP-PMLE CGP-ACE GCP-PCA}
  \cert{Amazon Web Services:\@ AWS-SAA AWS-SAP AWS-SOA AWS-DOP AWS-ANS AWS-DVA}
  \cert{Microsoft: Azure Fundamentals}
  \cert{Oracle:\@ OCA Java SE 8}
  \cert{CompTIA:\@ Server+ Network+ Cloud+ LPIC-1}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %
  %     COLUMN TWO
  %
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\begin{minipage}[t]{0.03\textwidth}
  \hspace{1em}
\end{minipage}
\begin{minipage}[t]{0.66\textwidth}

  %
  % EXPERIENCE
  %
  \intro{Multidisciplinary professional with strong business acumen (MBA,
    Economist, Marketing) and deep technical expertise (Telecom
    Engineer, MSc Computer Science, full stack in AI, Cloud Native and Cyber).
    Bringing value through technology by delivering mission-critical
    large-scale digital
    systems in several countries (Air Mobility Systems) and creating
    innovative products (ATM Digital Twin).
  }

  \section{Experience}

  \role{2024}{AI Advisor}{Thales Digital Factory}{Singapore}
  \detail{
    AI strategy, industrialisation and MLOps for Airspace Mobility
    Solutions and Thales Research and Technology. Two
    papers
    \href{https://www.sesarju.eu/sites/default/files/documents/sid/2024/papers/SIDs_2024_paper_077\%20final.pdf}{[1]}
    \href{https://www.sesarju.eu/sites/default/files/documents/sid/2024/papers/SIDs_2024_paper_090\%20final.pdf}{[2]}
    selected
    for SESAR Innovation Days.
  }
  \sectionsep{}

  \role{2024}{XCS229 Machine Learning Course Facilitator}{STANFORD
    ENGINEERING CENTER FOR
  GLOBAL \& ONLINE EDUCATION}{USA}
  \sectionsep{}

  \role{2021\(-\)24}{CHIEF PRODUCT OWNER AIR TRAFFIC MANAGEMENT
  DIGITAL TWIN}{Thales Airspace Mobility Solutions}{Singapore}
  \detail{
    Ideated, designed and built the first Digital Twin in the Air
    Traffic Management domain. First live
    trials of Continuous Descent Operations in Singapore Changi
    airport. Three successful negotiations and funding rounds with
    the National Research Foundation of Singapore. DG Award 2022
    (Outstanding) CAAS, Civil Aviation Authority of Singapore.
    Minister's Innovation (MI) Award 2022 (Distinguished Award),
    MOT, Ministry of Transport Singapore.
  }
  \sectionsep{}

  \role{2020}{DIGITAL INFRASTRUCTURE \& DEPLOYMENT DIRECTOR}{Thales
  Airspace Mobility Solutions}{Australia}
  \sectionsep{}

  \role{2017\(-\)19}{ONESKY INFRASTRUCTURE \& DEPLOYMENT PROJECT
  DIRECTOR}{Thales Airspace Mobility Solutions}{Australia}
  \sectionsep{}

  \role{2016}{CONTRACT \& PM ADVISOR}{ADELTE}{Spain \& Pakistan}
  \sectionsep{}

  \role{2016}{AIRPORT SYSTEMS DIRECTOR}{ULTRA ELECTRONICS}{Brazil}
  \sectionsep{}

  \role{2013\(-\)15}{PROJECT DIRECTOR MC6 MASTER SYSTEMS INTEGRATOR
  MUSCAT AND SALALAH AIRPORTS}{ULTRA ELECTRONICS}{Oman}
  \sectionsep{}

  \role{2011\(-\)12}{DIRECTOR AIR TRAFFIC MANAGEMENT \& AIRPORTS
  INDIA}{INDRA SISTEMAS}{India}
  \sectionsep{}

  \role{2009\(-\)10}{AIRPORT IT PM}{INDRA SISTEMAS}{Spain}
  \sectionsep{}

  \role{2009\(-\)10}{IT EXPERT COUNSEL}{BAKER \& MCKENZIE}{Spain}
  \sectionsep{}

  \role{2002\(-\)09}{PROGRAMME MANAGER IT SYSTEMS, INTEGRATION \&
  SECURITY BARCELONA AIRPORT EXPANSION}{AENA}{Spain}
  \sectionsep{}

  \role{2001\(-\)02}{TRANSPORT IT SENIOR CONSULTANT}{ADVANCED
  LOGISTICS GROUP}{Spain}
  \sectionsep{}

  \role{2000}{SUPPLY CHAIN MANAGEMENT RESEARCHER}{IESE BUSINESS SCHOOL}{Spain}
  \sectionsep{}

  \role{1995\(-\)99}{ENTREPRENEUR}{GLOBALCOM \& COMMFACTORY}{Spain}
  \sectionsep{}

\end{minipage}
\end{document}  \documentclass[]{article}
